Secure Composition of Robust and Optimising Compilers

### 2024-09-12 tech/main.tex
more daitl

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP-Universal]{rtp-universal-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-comp1}{\rtpUniversal{\ccSI}{\mapUniversal{\sim_2}{\trgClass[_1]}}{\sim_1}}
    \asm{rtp-universal-compo-comp2}{\rtpUniversal{\ccIT}{\trgClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-compo}{\rtpUniversal{\fncompo{\ccSI}{\ccIT}}{\trgClass[_1]\cap\trgClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
  \end{goals}
\end{lemma}
\begin{proof}
  \incompleteProof
\end{proof}

@@

>>>>

\begin{definition}{\definitionlabel[Closedness w.r.t. Universal Image]{universal-map-wf}}
  \[
    \mapUniversalWF{\sim}{\trgClass} \isdef \forall \trgProperty\in\trgClass, \mapUniversal{\sim}{\trgProperty}\in\mapUniversal{\sim}{\trgClass}
  \]
\end{definition}
\begin{definition}{\definitionlabel[Closedness w.r.t. Existential Image]{existential-map-wf}}
  \[
    \mapExistentialWF{\sim}{\srcClass} \isdef \forall \srcProperty\in\srcClass, \mapExistential{\sim}{\srcProperty}\in\mapExistential{\sim}{\srcClass}
  \]
\end{definition}

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP-Universal]{rtp-universal-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-wfsig}{\mapUniversalWF{\sim_2}{\trgClass[_1]}}
    \asm{rtp-universal-compo-comp1}{\rtpUniversal{\ccSI}{\mapUniversal{\sim_2}{\trgClass[_1]}}{\sim_1}}
    \asm{rtp-universal-compo-comp2}{\rtpUniversal{\ccIT}{\trgClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-compo}{\rtpUniversal{\fncompo{\ccSI}{\ccIT}}{\trgClass[_1]\cap\trgClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
  \end{goals}
\end{lemma}
\begin{proof}
  \incompleteProof
\end{proof}

@@

To conclude a similar colloray as \corollaryref{rtp-swappable}, it is of great use to show that a given cross-language trace relation has no effect on the class of security properties.
Then, it is possible to derive the following consequences:

\begin{corollary}[\Coqed]{\lemmalabel[Commutativity of RTP-Universal]{rtp-universal-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-wfsig1}{\mapUniversalWF{\sim_1}{\irlClass[_2]}}
    \asm{rtp-universal-compo-wfsig2}{\mapUniversalWF{\sim_2}{\irlClass[_1]}}
    \asm{rtp-universal-compo-eq2}{\mapUniversal{\sim_2}{\irlClass[_1]}=\irlClass[_1]}
    \asm{rtp-universal-compo-eq1}{\mapUniversal{\sim_1}{\irlClass[_2]}=\irlClass[_2]}
    \asm{rtp-universal-swappable-comp1}{\rtpUniversal{\ccII}{\irlClass[_1]}{\sim_1}}
    \asm{rtp-universal-swappable-comp2}{\rtpUniversal{\ccII[\delta]}{\irlClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-swappable1}{\rtpUniversal{\fncompo{\ccII}{\ccII[\delta]}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
    \goal{rtp-universal-swappable2}{\rtpUniversal{\fncompo{\ccII[\delta]}{\ccII}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_2}{\sim_1}}}
  \end{goals}
\end{corollary}
\begin{proof}
  todo
\end{proof}

\begin{corollary}[\Coqed]{\lemmalabel[Commutativity of RTP-existential]{rtp-existential-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-existential-compo-wfsig1}{\mapExistentialWF{\sim_1}{\irlClass[_2]}}
    \asm{rtp-existential-compo-wfsig2}{\mapExistentialWF{\sim_2}{\irlClass[_1]}}
    \asm{rtp-existential-compo-eq2}{\mapExistential{\sim_2}{\irlClass[_1]}=\irlClass[_1]}
    \asm{rtp-existential-compo-eq1}{\mapExistential{\sim_1}{\irlClass[_2]}=\irlClass[_2]}
    \asm{rtp-existential-swappable-comp1}{\rtpExistential{\ccII}{\irlClass[_1]}{\sim_1}}
    \asm{rtp-existential-swappable-comp2}{\rtpExistential{\ccII[\delta]}{\irlClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-existential-swappable1}{\rtpExistential{\fncompo{\ccII}{\ccII[\delta]}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
    \goal{rtp-existential-swappable2}{\rtpExistential{\fncompo{\ccII[\delta]}{\ccII}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_2}{\sim_1}}}
  \end{goals}
\end{corollary}
\begin{proof}
  todo
\end{proof}

if $\sim_1,\sim_2:\irl{I}\to\irl{I}$ are galois, then simpler commutativity
